Turbo fast no compromise gravitational wave parameter estimation

### 2023-01-10 src/tex/ms.tex
Add real event parameter estimation

% State the distribution of injected population
We sample 1000 events from the following distribution of parameters detailed in
table \ref{tab:parameters}.
The same distribution of parameters are used as the prior in the PE process.
The simulated signals have a 16 seconds segment length,
and we project the signal on the LIGO Hanford, Livingston and Virgo detector.
We used the designed sensitivity curve for each detector to generate the noise \kw{cite}.
We use a minimum frequency cutoff of 30 Hz with a sampling rate of 2048 Hz.

\begin{table}[hbt!]
    \begin{center}
    \begin{tabular}{ l l l }
    \hline
    \hline
    Parameters &  Description & Prior range\\

    $M_c$ & Chirp mass & $[10, 50] M_\odot$\\
    $q$ & Mass ratio & $[0.5, 1]$\\
    $\chi_1$ & Primary dimensionless spin& $[-0.5, 0.5]$\\
    $\chi_2$ & Secondary dimensionless spin & $[-0.5, 0.5]$\\
    $d_L$ & Luminosity distance & $[300, 2000] \textrm{Mpc}$\\
    $t_c$ & Coalescence time & $[-0.5, 0.5] \textrm{s}$\\
    $\phi_c$ & Coalescence phase & $[0, 2\pi]$\\
    $\cos{\iota}$ & Cosine of inclination angle & $[-1, 1]$\\
    $\psi$ & Polarization angle & $[0, \pi]$\\
    $\alpha$ & Right ascension & $[0, 2\pi]$\\
    $\sin{\delta}$ & Sine of declination & $[-1, 1]$\\

    \hline
    \hline
    \end{tabular}
    \caption{Parameters used in the injection-recovery test.}
    \label{tab:parameters}
    \end{center}
\end{table}

@@

To demonstrate the performance of our parameter estimation pipeline, we apply
our pipeline to analyze GW150914 and GW170817.

\kw{GW159014}

@@

\kw{GW170817}

@@

% Describe the distance between flowMC result and Bilby result using Jensen-Shannon divergence, scipy has a function to compute that in scipy.spatial.distance

>>>>

% State the distribution of injected population
We sample 1200 events from the following distribution of parameters detailed in
table \ref{tab:parameters}.
The same distribution of parameters are used as the prior in the PE process.
The simulated signals have a 16 seconds segment length,
and we project the signal on the LIGO Hanford, Livingston and Virgo detector.
We used the designed sensitivity curve for each detector to generate the noise \kw{cite}.
We use a minimum frequency cutoff of 30 Hz with a sampling rate of 2048 Hz.

\begin{table*}[hbt!]
    \begin{center}
    \begin{tabular}{ l l l l l }
    \hline
    \hline
    Parameters &  Description & Injection & GW150914 & GW170817\\

    $M_c$ & Chirp mass $[M_\odot]$& $[10, 50]$ & $[10,80]$ & $[1.18,1.21]$ \\
    $q$ & Mass ratio & $[0.5, 1]$ & $[0.125,1]$ & $[0.125,1]$ \\
    $\chi_1$ & Primary dimensionless spin& $[-0.5, 0.5]$ & $[-1,1]$ & $[-0.3,0.3]$ \\
    $\chi_2$ & Secondary dimensionless spin & $[-0.5, 0.5]$ & $[-1,1]$ & $[-0.3,0.3]$ \\
    $d_L$ & Luminosity distance $[\textrm{Mpc}]$ & $[300, 2000]$ & $[0, 2000]^\dag$ & $[1, 75]^\dag$ \\
    $t_c$ & Coalescence time $[\textrm{s}]$& $[-0.5, 0.5]$ & $[-0.1, 0.1]$ & $[-0.1, 0.1]$ \\
    $\phi_c$ & Coalescence phase & $[0, 2\pi]$ & $[0, 2\pi]$ & $[0, 2\pi]$ \\
    $\cos{\iota}$ & Cosine of inclination angle & $[-1, 1]$ & $[-1, 1]$ & $[-1, 1]$ \\
    $\psi$ & Polarization angle & $[0, \pi]$ & $[0, \pi]$ & $[0, \pi]$ \\
    $\alpha$ & Right ascension & $[0, 2\pi]$ & $[0, 2\pi]$ & $[0, 2\pi]$ \\
    $\sin{\delta}$ & Sine of declination & $[-1, 1]$ & $[-1, 1]$ & $[-1, 1]$ \\

    \hline
    \hline
    \end{tabular}
    \caption{Parameters used and the range of prior for the injection-recovery
    test, GW150914, and GW170817. All priors assume a uniform distribution with
    the range tabulated in the table. The coalescence time refers to a shift in
    time around the trigger time. $^\dag$ Instead of uniform in luminosity
    distance, the distance prior used for the GW150914 and GW170817 analysis are
    uniform in comoving distance, with the range denote by the value in the
    table in $\textrm{MPC}$}
    \label{tab:parameters}
    \end{center}
\end{table*}

@@

To demonstrate the performance of our parameter estimation pipeline, we apply
our pipeline to analyze GW150914 and GW170817. The prior used for the two events
are shown in table \ref{tab:parameters}. We use a 4 seconds long segment for the
GW150914 analysis, and a 128 seconds long segment for the GW170817 analysis.
Both data segment are fetched from GWOSC \kw{cite}. Given the specific sampler
setting we use, we produce around an average of 2500 and 3500 \textbf{effective
samples} for GW150914 and GW170817 \footnote{Note that effective sample measures
the number of independent samples, which takes correlation between step into
account, and it is not the same as the number of generated samples. The
effective sample size is computed using
\texttt{arviz},\url{https://python.arviz.org/en/stable/api/generated/arviz.ess.html}.}
in each analysis respectively, which is run on an Nvidia A100 GPU. The
\texttt{wall} time for both event is around 10 minutes. The chain data and the
analysis scripts which generate the chains can be found on
%\kw{\variable{data/} and \variable{script}}
. Most of the time is spent on jit compilation of the code, and the actual
sampling time was about \~150s. Note that we have pre-computed the reference
waveform parameters used in hetetrodyne likelihood for the two events, so the
time spent on solving for the reference waveform parameters is omitted in the
\texttt{wall} time calculation.

@@

@@

Since we are using the \texttt{IMRPhenomD} waveform and the open data release
available on GWOSC \kw{cite} does not provide the posterior samples for this
waveform, we run Bilby using the same prior and waveform model as a reference
for comparison. From fig \ref{fig:GW150914} and \ref{fig:GW170817}, we can see
the 11-dimensional posteriors results produced by our pipeline are consistent
with the results obtained using Bilby \kw{cite}.

% Describe the distance between flowMC result and Bilby result using
% Jensen-Shannon divergence, scipy has a function to compute that in
% scipy.spatial.distance
